Empirical normative theories

### 2020-08-02 simple.tex
Effective comparison (and a few other things)

\subsection{Classify propositions}
\begin{axiom}[Normative adequacy]
	\label{ax:norm}
	$\forall i \in I, \phi \in \Phi: 
		[(\exists \ar \in \allargs \suchthat \ar \ileadstost \phi) \land ¬(\exists \ar \in \allargs \suchthat \ar \ileadstost ¬\phi)] ⇒ \phi \in \iPhi \land ¬\phi \notin \iPhi.$
\end{axiom}
This axiom can be simplified, thanks to the following proposition.
\begin{proposition}[Protocol coherence]
	\label{prop:protcoh}
	$\forall i \in I, \phi \in \Phi$:
	\begin{equation}
		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstost ¬\phi].
	\end{equation}
\end{proposition}
\begin{proof}
	Protocol coherence is satisfied by definition of $\ileadstost$. Indeed, if for some $\ar \in \allargs$, $\ar \ileadstost \phi$, then $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadsto ¬\phi$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstost ¬\phi$ is false, because it requires that $\forall \ar_1 \in \allargs: (\ar', \ar_1) \ileadsto ¬\phi$, and thus in particular, that $(\ar', \ar) \ileadsto ¬\phi$.
\end{proof}

@@

\subsection{Non-completeness}
\begin{definition}[Theory completeness]
	$\forall \phi \in \Phi: [\exists \ar \in \allargs \suchthat \ar \ileadsto \phi] \lor [\exists \ar \in \allargs \suchthat \ar \ileadsto ¬\phi]$.
\end{definition}
\begin{definition}[Unrestricted interpretability]
	$\forall \phi \in \Phi: \phi \in \iPhi \oplus ¬\phi \in \iPhi$.
\end{definition}
\begin{definition}[Deliberation completeness]
	$\forall \phi \in \Phi: \phi \in \iPhi \lor ¬\phi \in \iPhi$.
\end{definition}
The following proposition directly follows from the definitions, together with \cref{prop:protcoh}.
\begin{proposition}
	1) Under Normative adequacy, Theory completeness implies Deliberation completeness. 2) Unrestricted interpretability implies Deliberation completeness.
\end{proposition}
Theories as defined here do not mandate Theory completeness. This is good for two reasons. First, even the weaker Deliberation completeness can be considered too strong. Second, it is dubious that, for non trivial decision problems, theories can be found for which both Normative adequacy is normatively compelling and Theory completeness holds.

@@

\begin{remark}
	Equivalently, $\df(\ar_0) = \powersetz{\dbeatsinv \circ \gbeatsinv}$. First, $\forall \args \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0): \dargs = \dbeatsinv(\args) \in \powersetz{\dbeatsinv \circ \gbeatsinv}$. Indeed, $\ar_1 \in \args$ thus $\ar_1 \gbeats \ar_0$, hence, $\ard \dbeats \ar_1$ (as mandated by ${\dbeats}$), thus $\dargs ≠ \emptyset$; and $\ard \in \dargs$ thus $\ard \dbeats \ar_1 \in \args$ thus $\ar_1 \gbeats \ar_0$. Second, $\dargs \in \powersetz{\dbeatsinv \circ \gbeatsinv} ⇒ \exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \suchthat \dbeatsinv(\args) = \dargs$. Defining $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar_0)$, $\dbeatsinv(\args) = \dargs$: considering $\ard \in \dargs$, $\ard \dbeats \ar_1 \gbeats \ar_0$, $\ar_1 \in \args$, $\ard \in \dbeatsinv(\ar_1)$, thus, $\ard \in \dbeatsinv(\args)$; and considering $\ard \in \dbeatsinv(\args)$, $\ard \dbeats \ar_1 \in \args$, $\ar_1 \gbeats \ar_0$, thus, $\ard \in \dargs$. That $\args ≠ \emptyset$ follows from $\dargs ≠ \emptyset$.
\end{remark}

An empirical theory must satisfy
$\exists k \in \N \suchthat \dfp^k(\gleadstoinv(\Phi)) = \emptyset$, where $\dfp^0$ is the identity function over $\allargs$.

@@

Given $i \in I, \phi \in \Phi, \ar_0 \in \allargs$ and $\args \subseteq \gbeatsinv(\ar_0)$, define $\args \ibeats \ar_0$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar_0) \cap \hist \land \ar_0 \in \histend \land \hist \nileadstost \phi$.

Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \powersetz{\alldargs}$, as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \land \args \ibeats \ar_0}$. 
Observe that $\di(\ar) \subseteq \df(\ar)$.
Define $\dip \subseteq \allargs × \allargs$ as $\dip(\ar) = \set{(\ar + \dargs) \suchthat \dargs \in \di(\ar)}$.
Given $i \in I, \phi \in \gPhi$, define $\gargs \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$.

$\ar$ $i$-defends $\phi$ iff $\emptyset \nibeats \ar$.

@@

A \emph{falsification instance} of an empirical theory is a tuple $(i, \phi, \hist) \in I × \gPhi × \allhist$ such that $\exists \ar \in (\histend \cap \gargs) \suchthat \gbeatsinv(\ar) \cap \hist = \emptyset \land \hist \nileadstost \phi$.

\begin{theorem}
	An empirical theory is convincing iff it has no falsification instances.
\end{theorem}
\begin{proof}
	For all $i \in I, \phi \in \gPhi$: $\exists \ar \in \gargs$ that does not $i$-defend $\phi$ iff $\exists \ar \in \gargs, \hist \in \allhist \suchthat \left[\ar \in \histend \land \gbeatsinv(\ar) \cap \hist = \emptyset \land \hist \nileadstost \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist)$ is a falsification instance.
\end{proof}

@@

	To prove the theorem, build a finite sequence of arguments in $\gargs$, starting with any $\ar_0 \in \gleadstoinv(\phi)$. Observe that $\ar_0 \in \gargs$. Given $k \in 2\N$, if $\ar_k \nileadstost \phi$, define $\ar_{k + 2}$ using the deduction following the lemma, obtaining $\ar_{k + 2} \in \gargs \cap \dfp^\frac{k + 2}{2}(\ar_0)$. 
	By definition of an empirical theory, $\exists k \in \N \suchthat \dfp^k(\ar_0) = \emptyset$, thus, this process ends with some $\ar$ such that $\ar \ileadstost \phi$.
\end{proof}

\subsection{Effectively comparing models}
Given a normative theory, consider two empirical theories $(q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, \alldargs, \dbeats, +)$ and $(q', (\gleadsto[q(i)][\delta])_{q(i) \in q(I)}, \gbeats', \alldargs, \dbeats', +')$.

Given a normative theory and $\phi \in \Phi$, say that two empirical theories (for that normative theory) disagree about $\phi$ iff $\phi \in \gPhi \land ¬\phi \in \gPhi[\delta]$.

If $\gamma$ and $\delta$ agree about all $\phi$, there is nothing to test as the theories are compatible. Otherwise, here is a test procedure that falsifies at least one of these theories, given any $\phi \in \Phi$ about which they disagree and any $i \in I$.

@@

\begin{remark}
	Informal idea.
	Consider $\ar_0 \in \allargs \suchthat \ar_0 \gleadsto \phi$. Test whether $(\ar_0) \ileadstost \phi$. If not, $(i, \phi, (\ar_0))$ is a falsification instance of $\gamma$. If $(\ar_0) \ileadstost \phi$, check whether some $\ar_1 \dbeats' \ar_0$. If not, $\delta$ is falsified? ($\ar_0$ attacks $\delta$ but $\delta$ is not able to defend.)…
\end{remark}

Lemma (variant of a previous one). $\ar_0$ $i$-defends $\phi$, and $\hist \nileadstost \phi$ with $\ar_0 \in \histend$, thus $\dargs = \dbeatsinv(\gbeatsinv(\ar_0) \cap \hist) \in \di(\ar_0)$, thus $\ar_2 = \ar_0 + \dargs \in \gargs \cap \dfp(\ar_0)$.

Consider $(…, \ar_0) \ileadstost \phi$ and $\hist = (…, \ar_0, \ar_{-1}) \nileadstost ¬\phi$, with $\ar_0 \in \gargs, \ar_{-1} \in \gargs[¬\phi]$. By the lemma (applied on $\ar_{-1}$), $\ar_1 = \ar_{-1} + \dbeatsinv(\gbeatsinv(\ar_{-1}) \cap \hist) \in \gargs[¬\phi] \cap \dfp(\ar_{-1})$. Iterating if necessary, we obtain $(…, \ar_1) \ileadstost ¬\phi$. Now either already the previous step was $(…, \ar_0, \ar_1)$, or we test $(…, \ar_1, \ar_0)$. If $(…, \ar_1, \ar_0) \ileadstost \phi$, apply the lemma again on $\ar_1$, and go on. Finally: $\hist = (…, \ar_1, \ar_0) \nileadstost \phi$. Similarly, then, obtain $\ar_2 = \ar_0 + \dargs \in \gargs \cap \dfp(\ar_0)$. If $\ar_0 \in (\dfp)^k(…)$, then $\ar_2 \in (\dfp)^{k'}(…)$, with $k' > k$. And $(…, \ar_2, \ar_1) \nileadstost ¬\phi$, so we can apply the strating step again.

>>>>

\subsection{Classify propositions}
\begin{axiom}[Normative adequacy]
	\label{ax:norm}
	$\forall i \in I, \phi \in \Phi: 
		[(\exists \ar \in \allargs \suchthat \ar \ileadstost \phi) \land ¬(\exists \ar \in \allargs \suchthat \ar \ileadstost ¬\phi)] ⇒ \phi \in \iPhi \land ¬\phi \notin \iPhi.$
\end{axiom}
This axiom can be simplified, thanks to the following proposition.
\begin{proposition}[Protocol coherence]
	\label{th:protcoh}
	$\forall i \in I, \phi \in \Phi$:
	\begin{equation}
		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstost ¬\phi].
	\end{equation}
\end{proposition}
\begin{proof}
	Protocol coherence is satisfied by definition of $\ileadstost$. Indeed, if for some $\ar \in \allargs$, $\ar \ileadstost \phi$, then $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadsto ¬\phi$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstost ¬\phi$ is false, because it requires that $\forall \ar_1 \in \allargs: (\ar', \ar_1) \ileadsto ¬\phi$, and thus in particular, that $(\ar', \ar) \ileadsto ¬\phi$.
\end{proof}

@@

\subsection{Non-completeness}
\begin{definition}[Theory completeness]
	$\forall \phi \in \Phi: [\exists \ar \in \allargs \suchthat \ar \ileadsto \phi] \lor [\exists \ar \in \allargs \suchthat \ar \ileadsto ¬\phi]$.
\end{definition}
\begin{definition}[Unrestricted interpretability]
	$\forall \phi \in \Phi: \phi \in \iPhi \oplus ¬\phi \in \iPhi$.
\end{definition}
\begin{definition}[Deliberation completeness]
	$\forall \phi \in \Phi: \phi \in \iPhi \lor ¬\phi \in \iPhi$.
\end{definition}
The following proposition directly follows from the definitions, together with \cref{th:protcoh}.
\begin{proposition}
	1) Under Normative adequacy, Theory completeness implies Deliberation completeness. 2) Unrestricted interpretability implies Deliberation completeness.
\end{proposition}
Theories as defined here do not mandate Theory completeness. This is good for two reasons. First, even the weaker Deliberation completeness can be considered too strong. Second, it is dubious that, for non trivial decision problems, theories can be found for which both Normative adequacy is normatively compelling and Theory completeness holds.

@@

\begin{remark}
	Equivalently, $\df(\ar_0) = \powersetz{\dbeatsinv \circ \gbeatsinv}$. 
	First, $\forall \args \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0): \dargs = \dbeatsinv(\args) \in \powersetz{\dbeatsinv \circ \gbeatsinv}$. 
	Indeed, $\ar_1 \in \args$ thus $\ar_1 \gbeats \ar_0$, hence, $\ard \dbeats \ar_1$ (as mandated by ${\dbeats}$), thus $\dargs ≠ \emptyset$; and $\ard \in \dargs$ thus $\ard \dbeats \ar_1 \in \args$ thus $\ar_1 \gbeats \ar_0$. 
	Second, $\dargs \in \powersetz{\dbeatsinv \circ \gbeatsinv} ⇒ \exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \suchthat \dbeatsinv(\args) = \dargs$. 
	Defining $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar_0)$, we see that $\dbeatsinv(\args) = \dargs$: considering $\ard \in \dargs$, $\ard \dbeats \ar_1 \gbeats \ar_0$, $\ar_1 \in \args$, $\ard \in \dbeatsinv(\ar_1)$, thus, $\ard \in \dbeatsinv(\args)$; and considering $\ard \in \dbeatsinv(\args)$, $\ard \dbeats \ar_1 \in \args$, $\ar_1 \gbeats \ar_0$, thus, $\ard \in \dargs$. 
	That $\args ≠ \emptyset$ follows from $\dargs ≠ \emptyset$.
\end{remark}

An empirical theory must satisfy
$\exists k \in \N \suchthat (\dfp)^k(\gleadstoinv(\Phi)) = \emptyset$, where $(\dfp)^0$ is the identity function over $\allargs$.

@@

Given $i \in I, \phi \in \Phi, \ar \in \allargs$ and $\args \subseteq \gbeatsinv(\ar)$, define $\args \ibeats \ar$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar) \cap \hist \land \ar \in \histend \land \hist \nileadstost \phi$.

Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \powersetz{\alldargs}$, as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \land \args \ibeats \ar}$. 
Observe that $\di(\ar) \subseteq \df(\ar)$.
Define $\dip \subseteq \allargs × \allargs$ as $\dip(\ar) = \set{(\ar + \dargs) \suchthat \dargs \in \di(\ar)}$.
Given $i \in I, \phi \in \gPhi$, define $\gargs \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$.

I write that $\ar$ \emph{$i$-defends} $\phi$ to mean that $\emptyset \nibeats \ar$.

@@

A \emph{falsification instance} of an empirical theory is a tuple $(i, \phi, \hist, \ar) \in I × \gPhi × \allhist × \gargs$ such that $\gbeatsinv(\ar) \cap \hist = \emptyset \land \ar \in \histend \land \hist \nileadstost \phi$. 
I also write that $(i, \phi, \hist, \ar)$ falsifies $\gamma$ to mean that it is a falsification instance of $\gamma$.

\begin{theorem}
	An empirical theory is convincing iff it has no falsification instances.
\end{theorem}
\begin{proof}
	For all $i \in I, \phi \in \gPhi, \ar \in \gargs$: $\ar$ does not $i$-defend $\phi$ iff $\exists \hist \in \allhist \suchthat \left[\gbeatsinv(\ar) \cap \hist = \emptyset \land \ar \in \histend \land \hist \nileadstost \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist, \ar)$ falsifies $\gamma$. Therefore, $\gamma$ is not convincing iff $\exists (i, \phi, \ar) \suchthat \ar$ does not $i$-defend $\phi$ iff $\exists \hist \suchthat (i, \phi, \hist, \ar)$ falsifies $\gamma$ iff $\gamma$ has a falsification instance.
\end{proof}

@@

	To prove the theorem, build a finite sequence of arguments in $\gargs$, starting with any $\ar_0 \in \gleadstoinv(\phi)$. Observe that $\ar_0 \in \gargs$. Given $k \in 2\N$, if $\ar_k \nileadstost \phi$, define $\ar_{k + 2}$ using the deduction following the lemma, obtaining $\ar_{k + 2} \in \gargs \cap (\dfp)^\frac{k + 2}{2}(\ar_0)$. 
	By definition of an empirical theory, $\exists k \in \N \suchthat (\dfp)^k(\ar_0) = \emptyset$, thus, this process ends with some $\ar$ such that $\ar \ileadstost \phi$.
\end{proof}

\subsection{Effectively comparing models}
\begin{lemma}
	\label{th:produce}
	Given $\phi \in \Phi$, $\ar_0 \in \allargs$ that $i$-defends $\phi$, and $\hist \nileadstost \phi$ with $\ar_0 \in \histend$, define $\args =  \gbeatsinv(\ar_0) \cap \hist$, $\dargs = \dbeatsinv(\args)$, and $\ar_2 = \ar_0 + \dargs$. Then, $\ar_2 \in \gargs \cap \dfp(\ar_0)$.
\end{lemma}
\begin{proof}
	Because $\dargs \in \di(\ar_0)$.
\end{proof}

Given $\phi \in \Phi$ and two empirical theories $\gamma$ and $\delta$ for a given normative theory, say that they disagree about $\phi$ iff $\phi \in \gPhi[\gamma] \land ¬\phi \in \gPhi[\delta]$. Say that they are incompatible iff there is at least one $\phi \in \Phi$ that they disagree about.

Given $\phi \in \Phi$, $\hist \in \allhist$ and $\ar_\gamma \in \gargs$, say that $(\hist, \ar_\gamma)$ challenges $(\gamma, \phi)$ iff $\hist \nileadstost \phi$ and $\ar_\gamma \in \histend$.
Given $\phi \in \Phi, \ar_\gamma \in \gargs, \ar_\delta \in \gargsdelta$, say that $(\hist, \ar_\gamma, \ar_\delta)$ is a $(\gamma, \phi$ or $\delta, ¬\phi)$-challenge iff $(\hist, \ar_\gamma)$ challenges $(\gamma, \phi)$ or $(\hist, \ar_\delta)$ challenges $(\delta, ¬\phi)$. \commentOC{This should be called a $\phi$-or-$¬\phi$-challenge.}

\begin{lemma}
	\label{th:endchal}
	Given $\ar_\gamma \in \gargs$, $\ar_\delta \in \gargsdelta$ and $\hist \in \allhist$ such that $\set{\ar_\gamma, \ar_\delta} \subseteq \histend$: $(\hist, \ar_\gamma, \ar_\delta)$ is a $(\gamma, \phi$ or $\delta, ¬\phi)$-challenge.
\end{lemma}
\begin{proof}
	Either $\hist \nileadstost \phi$, and $(\hist, \ar_\gamma, \ar_\delta)$ challenges $(\gamma, \phi)$, or $\hist \ileadstost \phi$, hence, by \cref{th:protcoh}, $\hist \nileadstost ¬\phi$, and $(\hist, \ar_\gamma, \ar_\delta)$ challenges $(\delta, ¬\phi)$. 
\end{proof}

\begin{lemma}
	\label{th:nextchal}
	Given $(\hist, \ar_\gamma)$ challenging $(\gamma, \phi)$, with $\ar_\gamma \in \gargs \cap \dfpclosure$, and $\ar_\delta \in \gargsdelta$: either $(i, \phi, \hist, \ar_\gamma)$ falsifies $\gamma$, or there exists a $(\gamma, \phi$ or $\delta, ¬\phi)$-challenge $(\histp, \ar'_\gamma, \ar_\delta)$, with $\ar'_\gamma \in \gargs \cap (\dfp)^{k + 1}(\gleadstoinv(\phi))$.
\end{lemma}
\begin{proof}
	If $\ar_\gamma$ does not $i$-defend $\phi$, then $(i, \phi, \hist, \ar_\gamma)$ falsifies $\gamma$, which ends the proof. 
	Thus, assume that $\ar_\gamma$ $i$-defends $\phi$.

	\Cref{th:produce} applies and yields $\ar'_\gamma = \ar_\gamma + \dbeatsinv(\gbeatsinv(\ar_\gamma)) \in \gargs \cap \dfp(\ar_\gamma)$, thus $\ar'_\gamma \in (\dfp)^{(k + 1)}(\gleadstoinv(\phi))$. 
	Now, define $\histpp = (\hist, \ar'_\gamma)$ and test whether $\histpp \nileadstost \phi$.

	If $\histpp \nileadstost \phi$, define $\histp = \histpp$, and observe that $(\histp, \ar'_\gamma, \ar_\delta)$ challenges $(\gamma, \phi)$, which concludes the proof. 
	Thus, assume that $\histpp \ileadstost \phi$.

	Let us now define $\histp$ such that $\set{\ar'_\gamma, \ar_\delta} \subseteq \histpend$, so that \cref{th:endchal} applies on $(\histp, \ar'_\gamma, \ar_\delta)$, which will conclude the proof.

	If $\ar_\delta \in \histppend$, this is done by defining $\histp = \histpp$. Otherwise, define $\histp = (\histpp, \ar_\delta)$ and test whether $\histp \nileadstost \phi$. 
\end{proof}

Given a normative theory and two empirical theories for that normative theory and $i \in I$, 
a \emph{test procedure with $i$} is a finite sequence $({\hist}^k)_{k \in \intvl{1, N}}$, for some $N \in \N^*$, of sequences of arguments, 
such that $\forall k \in \intvl{2, N}, {\hist}^k$ starts with ${\hist}^{k-1}$, and 
such that $(i, \phi, {\hist}^N)$ falsifies one of the empirical theories for some $\phi \in \Phi$. 
A sequence of arguments $\histp$ starts with a sequence of arguments $\hist$ of length $l$ iff $\histp$ has length at least $l$ and $\forall k \in \intvl{1, l}: \histp_k = \hist_k$.
\commentOC{Need the test procedure to be a tree. Atom: $(k, \phi)$ meaning whether ${\hist}^k \ileadstost \phi$. Branch label: atoms linked using or and and operators. From a node $n = (\hist, \ar, \phi)$, let branches depart, such that their labels do not overlap. From a node, if no branch label is true, the node must falsify a theory. In the case of the procedure below, it is not a list because we may query several times the same theory or switch to the other one, depending on the last answer. But if simplifying the theory (single-try), we may then simplify the definition of a test procedure.}

\begin{theorem}
	Given two incompatible empirical theories for a given normative theory, $\alpha = (q, (\gleadsto[q(i)][\alpha])_{q(i) \in q(I)}, \gbeats[\alpha], \alldargs, \dbeats[\alpha], +_\alpha)$ and $\beta = (q', (\gleadsto[q(i)][\beta])_{q(i) \in q(I)}, \gbeats[\beta], \alldargs, \dbeats[\beta], +')$ and given any $i \in I$, there exists a test procedure with $i$ that falsifies one of these theories.
\end{theorem}
\begin{proof}
	Pick any $\phi \in \Phi$ about which $\alpha$ and $\beta$ disagree.

	Given $k_\alpha, k_\beta \in \N, \hist \in \allhist, \ar_\alpha \in \gargsalpha, \ar_\beta \in \gargsbeta$, 
	say that 
	$(\hist, \ar_\alpha, \ar_\beta)$ is a challenge of complexity $(k_\alpha, k_\beta)$ iff 
	$(\hist, \ar_\alpha, \ar_\beta)$ is a $(\alpha, \phi$ or $\beta, ¬\phi)$-challenge, $\ar_\alpha \in (\dfp[\alpha])^{k_\alpha}(\gleadstoinv[\alpha](\phi))$, and $\ar_\beta \in (\dfp[\beta])^{k_\beta}(\gleadstoinv[\beta](¬\phi))$.

	Pick any $\ar_{-1} \in \allargs \suchthat \ar_{-1} \gleadsto[][\beta] ¬\phi$. Observe that $\ar_{-1} \in \gargsbeta \cap (\dfp[\beta])^0(\gleadstoinv[\beta](¬\phi))$. Test whether $(\ar_{-1}) \nileadstost \phi$. If so, $(i, \phi, (\ar_{-1}), \ar_{-1})$ falsifies $\beta$, which ends the procedure. 
	Thus, assume that $(\ar_{-1}) \ileadstost \phi$.

	Pick any $\ar_0 \in \allargs \suchthat \ar_0 \gleadsto[][\alpha] \phi$. Observe that $\ar_0 \in \gargsalpha \cap (\dfp[\alpha])^0(\gleadstoinv[\alpha](\phi))$.  Define $\hist = (\ar_{-1}, \ar_0)$ and test whether $\hist \nileadstost \phi$. By \cref{th:endchal}, $(\hist, \ar_0, \ar_{-1})$ is a $(\alpha, \phi$ or $\beta, ¬\phi)$-challenge, thus, $(\hist, \ar_0, \ar_{-1})$ is a challenge of complexity $(0, 0)$.

	Suffices now to apply \cref{th:nextchal} repetitively, until finding a falsification instance of $\alpha$ or $\beta$. This is because, given a challenge $(\hist, \ar_\alpha, \ar_\beta)$ of complexity $(k_\alpha, k_\beta)$, \cref{th:nextchal} applies, yielding either a falsification instance, or a new challenge of higher complexity. 
Indeed, if $(\hist, \ar_\alpha)$ challenges $(\alpha, \phi)$, apply \cref{th:nextchal} with $\alpha$ for $\gamma$, $\beta$ for $\delta$, and obtain either that $\hist$ falsifies $\alpha$, or a new tuple $(\histp, \ar'_\alpha, \ar_\beta)$ that is a challenge of complexity $(k_\alpha + 1, k_\beta)$.
And if $(\hist, \ar_\beta)$ challenges $(\beta, ¬\phi)$, apply \cref{th:nextchal} with $¬\phi$ for $\phi$, $\beta$ for $\gamma$, $\alpha$ for $\delta$, and obtain either that $\hist$ falsifies $\beta$, or a new tuple $(\histp, \ar'_\beta, \ar_\alpha)$ such that $(\histp, \ar_\alpha, \ar'_\beta)$ is a challenge of complexity $(k_\alpha, k_\beta + 1)$.

	Given that $\exists K_\alpha \suchthat (\dfp[\alpha])^{K_\alpha}(\gleadstoinv[\alpha](\phi)) = \emptyset$ and $K_\beta \suchthat (\dfp[\beta])^{K_\beta}(\gleadstoinv[\beta](¬\phi)) = \emptyset$ by definition of empirical theories, this process must end with a falsifying instance of $\alpha$ or $\beta$.
\end{proof}

@@

\subsection{TODO, about comparisons}
Count the number of tests; assume simpler theory.

Indicate sufficient hypothesis for ensuring that if a model resisted every attack, it is valid. Thus, that searching for falsification instances in the tested ones is enough.

\section{LS}
%Idea: argue for P > $.
%4 ways:
%- choose
%- rate attractivity: b1 → +; b2 → ++ thus b2 > b1
%- bids to buy (B-bid): I’d pay max $4 to buy and play b1; I’d pay max $6 to play b2 thus b2 > b1
%- bids to sell (S-bid): I’d sell b1 for at least $3; I’d sell b2 for at least $5 thus b2 > b1.
%
%First two: focus on probs. Last two: focus on amounts.
%
%Compare P = (.99, +$4; .01, −$0.1) VS $ = (.33, +$16; .67, −$2). Typically, choose P and bid more for $.
%E[P] ≈ $4; E[$] ≈ 5+1/3 − 4/3 = $4.
%
%XP1. Choice VS S-bid. No gambling. 6 P bets, 7 $ bets. 12 pairs, of which 6 presented in the table: (P, $), choose one, and indicate the strength of your preference (slight to very strong). Then 19 bets using S-big, 6 practice (other bets) then 13 were analyzed.
%
%E[P] and E[$] (of the example above) are similar, but bids “greatly exceeding the expected value of $3.94 are common”.
%
%XP2. Choice VS B-bid.
%
%XP3. With effective gambling and iterated thinking to thing about their preference.
Define $P = (.99, +\$4; .01, −\$0.1)$ and $D = (.33, +\$16; .67, −\$2)$.

Theory claims that all $i$’s prefer deliberately $P$ to $D$, in the sense of betting at least as much for.

Define $\phi$ as: $i$ deliberately prefers $P$ to $D$, in the sense of bidding at least as much for $P$ than for $D$ after deliberation. Define $¬\phi$ similarly, but bidding more for $D$ than for $P$.

Define $\ileadsto$ as follows. Given $\hist = (…, \ar)$, $\hist \ileadstost \phi$ iff, in a situation of $i$ having been exposed to the prefix …, saying: “Considering the argument $\ar$, would you please indicate your maximum selling price for $P$, and for $D$” leads $i$ to act accordig to $\phi$. Note that $\hist \ileadsto \phi$ iff $\hist \nileadsto ¬\phi$.

Thus, the normative axiom is satisfied iff, whenever there is a argument that, facing any counter-argument, leads $i$ to bid at least as much for $P$ than for $D$, we are ready to accept that $i$ deliberately prefers $P$ to $D$, in the bidding sense.

Define $\ar_0$ as arguing that the bid for both P and D should equal their expected revenue, namely, $.99 × (\$4) − 0.01 × \$0.1$ or etc. “Imagine you play this bet 100 times. On average, you will win 99 times and lose 1 time, which means gaining 99 × \$4 = \$396 and losing 1 × \$0.10 = \$0.10, hence a total net gain of \$395.90. Thus, your average net gain for the $P$ bet would be \$3.9590. Etc.”

Define $\ar_1$ as arguing that the utility of money should matter, not the revenue, and arguing that a loss hurts more than a gain. Define $\ar_2$ as arguing that the goal is to maximise average revenue, and thus, losses should count equally to gains. Define $\ar'_1$ as arguing by considering only what is to be gained and not the probabilities, and thus, arguing that $D$ is worth much more. Define $\ar'_2$ as arguing that also the probabilities should be taken into account.
Define $+$ as the simple concatenation of its arguments.

Then, define $\gbeats = \set{(\ar_1, \ar_0), (\ar'_1, \ar_0), (\ar'_1, \ar_2), (\ar_1, \ar'_2)}$, $\dbeats = \set{(\ar_2, \ar_1), (\ar'_2, \ar'_1)}$.

TODO consider using only $\phi$ being sure, and dropping everything related to possibility.
